---
title: "Standup NLP"
author: "David DeStephano"
date: "March 28, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r warning=FALSE}
library(tidyverse)
```


Inspired by these projects, one comparing gender deifferences between commencement speeches, and the other compariring standup specials 

https://towardsdatascience.com/using-nlp-to-explore-leadership-inspiration-f2e0b805d01c

https://medium.com/nwamaka-imasogie/stand-up-comedy-and-nlp-c7d64002520c

Lets pick 5 mens and 5 womens specials from the last 10 years from the most popular stand up specials on [IMDB](https://www.imdb.com/search/title/?title_type=tv_special&genres=comedy&explore=title_type,genres) with no repeating comedians. Was not sure if I should include Hannah Gadsby: [Nanette](https://scrapsfromtheloft.com/2018/07/21/hannah-gadsby-nanette-transcript/) or not because it is too serious


Men:
https://scrapsfromtheloft.com/2020/03/21/bert-kreischer-hey-big-boy-transcript/

https://scrapsfromtheloft.com/2020/03/12/marc-maron-end-times-fun-transcript/

https://scrapsfromtheloft.com/2020/03/01/pete-davidson-alive-from-new-york-transcript/

https://scrapsfromtheloft.com/2019/08/26/dave-chappelle-sticks-stones-transcript/

https://scrapsfromtheloft.com/2018/03/15/ricky-gervais-humanity-transcript/

https://scrapsfromtheloft.com/2020/03/25/tom-segura-ball-hog-transcript/


Women:
https://scrapsfromtheloft.com/2018/09/13/iliza-shlesinger-war-paint-transcript/

```{r}
tomlinson<-read.table("taylor_tomlinson.txt")

```

https://scrapsfromtheloft.com/2018/07/21/hannah-gadsby-nanette-transcript/

https://scrapsfromtheloft.com/2018/05/15/ali-wong-hard-knock-wife-full-transcript/

https://scrapsfromtheloft.com/2017/06/20/amy-schumer-leather-special-2017-full-transcript/

https://scrapsfromtheloft.com/2019/10/04/nikki-glaser-bangin-transcript/





